---
title: "HW3"
author: "Shihao Yang"
date: "9/27/2021"
output: github_document
---
# My github repo: (https://github.com/Hawk9808/433HW)
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(dplyr)
library(nycflights13)
library(ggplot2)
```

```{r}
orig_data <- flights
```

#### 1. How many flights have a missing dep_time? What other variables are missing? What might these rows represent?
```{r}
#How many flights have a missing dep_time?
# orig_data %>% 
#   summarise(miss_dep = sum(is.na(dep_time)))
 
#How many flights have a missing dep_time? What other variables are missing?
summary(flights)
  
```


>*As we can see from the above summary, 8255 flights have a missing `dep_time`, 8255 have a missing `dep_delay`, 8713 have a missing `arr_time`, 9430 have a missing `arr_delay`, and 9430 have a missing `air_time`. In a row with missing values, we can expect that this might be a flight that failed to depart or arrive. Also, this missing data could be just normally lost.*

#### 2. Currently dep_time and sched_dep_time are convenient to look at, but hard to compute with because they’re not really continuous numbers. Convert them to a more convenient representation of number of minutes since midnight.
```{r}
data_mutate <- orig_data %>% 
  mutate(dep_time = (dep_time %/% 100) * 60 + (dep_time %% 100),
         sched_dep_time = (sched_dep_time %/% 100) * 60 + (sched_dep_time %% 100))
head(data_mutate)
```

#### 3. Look at the number of canceled flights per day. Is there a pattern? Is the proportion of canceled flights related to the average delay? Use multiple dyplr operations, all on one line, concluding with ggplot(aes(x= ,y=)) + geom_point()
```{r}
data_3 <- orig_data %>%
  mutate(dep_date = lubridate::make_datetime(year, month, day)) %>%#this is consulting from r4ds_solution.
  group_by(dep_date) %>%
  summarise(cancel_flight = sum(is.na(dep_delay)), 
            total_num_flight = n(),
            dep_delay_mean = mean(dep_delay,na.rm=TRUE),
            arr_delay_mean = mean(arr_delay,na.rm=TRUE))

ggplot(data = data_3, aes(x= cancel_flight/total_num_flight)) + 
  geom_point(aes(y=dep_delay_mean), color='blue') + 
  geom_smooth(aes(y=dep_delay_mean), color='blue')+
  geom_point(aes(y=arr_delay_mean), color='red') + 
  geom_smooth(aes(y=arr_delay_mean), color='red')+
  ylab('mean delay time in min')
```


>*As we can see from the above graph, in many times, as cancellation rate increase, the average delay of that day also increase.*

